Working title: Mirkovi\'c--Vybornov fusion in Beilinson--Drinfeld Grassmannian

### 2020-12-23 main.tex
more lattice descriptions

@@

>>>>

Address limitations outside of type $A$?

@@

In ordinary $\Gr$ we have the following lattice descriptions valid only in type \(A\).  
%   Let \(T\) be a maximal torus. 
%   Denote \(\cO = \CC[t]\) and \(\cK =\CC(t) \).  
  Given \(\mu\in X^\bullet(T)\), write \(t^\mu\) for its image in \(G(\cK)\) and 
  % 
  % E.g.\ \(t^\mu = \diag (t^{\mu_1},\dots,t^{\mu_m})\) in \(GL_m(\cK)\)  and 
  \(L_\mu\) for its image in 
  \[
    \Gr = G(\cK)/G(\cO)  \overset{A}{=}  \{L\overset{\text{free}}{\underset{\text{rank } m}{\subset}} \cO^m : tL \subset L \}
  \]   % (orbit-stabilizer).
% 
Example: \(L_\mu = \Sp_{\cO}(e_it^j : 0\le j <\mu_i)\).  
  Fact: \(\Gr^T = X^\bullet(T)\)  
  and other distinguished subsets (needed for the definition of MV cycles and later open subset thereof) are all orbits of fixed points  
  \[
    \begin{aligned}
  % \Gr &= G(\cK)/G(\cO) & & = \{L\subset \CC[t]^m : tL \subset L \} \\
  \Gr^\lambda &= G(\cO) L_\lambda & & = \{L\in\Gr : t\big|_{\cO^m/L} \text{ has Jordan type } \lambda\} \\
      \Gr_\mu & = G_1[t^{-1}] L_\mu & & = \{L\in \Gr : L = \Sp_{\cO}(v_1,\dots,v_m) \text{ such that } \\
        & & & \qquad\quad  v_j = t^{\mu_j} e_j + \sum p_{ij} e_i \text{ with  } \deg p_{ij} < \mu_j \} \\
  S^\mu_- &= U_-(\cK) L_\mu & & = \{L\in \Gr_\mu : \dim (\cO^k / L\cap \cO^k) = \mu_1 + \dots + \mu_k \}
    \end{aligned}
  \]
